Subtle Gestures with the J!NS MEME

### 2021-08-14 Paper/paper.tex
Format lists and table

\subsection{Workflow}
We began with planning the rough outline that our research would follow.
The plan was as follows:
* Gather gesture ideas
* Check ideas for detectable responses
* Create tools to automate the recording of gestures
* Collect labelled data with the tools
* Model, train and validate a neural network until its performance is sufficient
* Test the network on our withheld test dataset

@@

\subsection{Gestures}
% TODO, maybe use self-made illustrations here
In the first phase, we came up with gestures we considered subtle. Early candidates were:
* Pushing your glasses up your nose [see GIF]
* A thinking pose, where you touch your chin with your thumb and your cheek with your
index finger [see GIF]
* Slow nodding [see GIF]
* Tapping the frame of the glasses [see GIF]

Since some of the gestures generated barely any responses on the EOG or the IMU readouts
[see figures with an example of a strong and a weak response],
we continued coming up with gestures until we had a total of seven gestures.
The gestures we came up with and their apparent responses can be seen in the following
table:

Pushing glasses up the nose | strong
Readjusting glasses | strong
Thinking pose | weak
Slow nodding | strong
Tilting head sideways | strong
Stroking mustache | weak
Biting lip | weak
Tapping on the nose | strong
Rubbing the nose | strong
Pushing cheek up with a finger | strong
Tapping the glasses | strong

>>>>

\subsection{Workflow}
We began with planning the rough outline that our research would follow.
The plan was as follows:
\begin{itemize}
    \item Gather gesture ideas
    \item Check ideas for detectable responses
    \item Create tools to automate the recording of gestures
    \item Collect labelled data with the tools
    \item Model, train and validate a neural network until its performance is sufficient
    \item Test the network on our withheld test dataset
\end{itemize}

@@

\subsection{Gestures}
% TODO, maybe use self-made illustrations here
In the first phase, we came up with gestures we considered subtle. Early candidates were:
\begin{itemize}
    \item Pushing your glasses up your nose [see GIF]
    \item A thinking pose, where you touch your chin with your thumb and your cheek with your
        index finger [see GIF]
    \item Slow nodding [see GIF]
    \item Tapping the frame of the glasses [see GIF]
\end{itemize}

Since some of the gestures generated barely any responses on the EOG or the IMU readouts
[see figures with an example of a strong and a weak response],
we continued coming up with gestures until we had a total of seven gestures.
The gestures we came up with and their apparent responses can be seen in table \ref{responses}.

\begin{table}
\caption{The quality of the EOG and IMU sensor responses for our gestures.}\label{responses}
\begin{tabular}{|l|l|}
    \hline
    Gesture description & Response quality\\
    \hline
    Pushing glasses up the nose & strong\\
    Readjusting glasses & strong\\
    Thinking pose & weak\\
    Slow nodding & strong\\
    Tilting head sideways & strong\\
    Stroking mustache & weak\\
    Biting lip & weak\\
    Tapping on the nose & strong\\
    Rubbing the nose & strong\\
    Pushing cheek up with a finger & strong\\
    Tapping the glasses & strong\\\hline
\end{tabular}
\end{table}
